Supplemental Materials: \emph{Simultaneous segmentation and registration of diffusion MR images of the brain driven by active-contours}

### 2015-04-04 Publications/2015-NeuroImage/03-introduction.tex
my changes

% -*- root: 00-main.tex -*-
\section{Introduction}\label{sec:introduction}
The accurate delineation of \gls*{wm} in \gls*{dmri} and the fusion of prior
  anatomical information extracted from a \gls*{t1} image of the same subject
  are crucial in a range of applications based on tractography, such as
  the extraction of structural connectivity \citep{craddock_imaging_2013} or
  tract-based spatial statistics \citep{smith_tractbased_2006}.
However, segmenting \gls*{dmri} data precisely and coregistration of anatomical
  images are difficult for several reasons.
First, \gls{dmri} images suffer from partial voluming of several tissues in 
  interfacing voxels due to the low resolution of images (generally around
  \isores[mm]{2.2}).
Second, \gls*{dmri} schemes probe the diffusion process within the brain in 
  many angles called \glspl*{dwi}, completed by one or more baseline (\emph{b0}) 
  volumes without directional gradients.
The extremely low \gls*{snr} and high dimensionality of \glspl*{dwi} disable their
  use for direct segmentation.
The contrast between \gls*{gm} and \gls*{wm} in the \emph{b0} volumes is not suitable for 
  segmentation either.
Finally, \gls*{dmri} images are acquired using \gls*{epi} to speed up acquisition
  at the cost of presenting geometrical distortion and 
  signal losses \citep{jezzard_correction_1995} that hinder the segmentation by
  registering an anatomical image as source of same-subject prior information.
The artifact has been proven to cause an important impact on the anatomy extracted
  from \gls*{dmri} \citep{irfanoglu_effects_2012}, particularly in certain fiber bundles
  when used in whole-brain tractography.

@@

To solve registration, \cite{saad_new_2009} used Pearson correlation to perform linear
  alignment of \gls*{t1} and \emph{b0}.
Another linear registration method is \emph{bbregister} \citep{greve_accurate_2009},
  uses active contours with edges to look for intensity boundaries in the \emph{b0}
  image.
The active contours are initialized by surfaces extracted from the 
  \gls*{t1} using \emph{FreeSurfer} \citep{fischl_freesurfer_2012}:
  the pial surface (exterior of cortical \gls*{gm}) and the \gls*{wm}/\gls*{gm} interface.
In practice, the \emph{b0} image only presents a detectable frontier for the pial surface
  and \emph{bbregister} is limited to align the cortical surface.
Since the distortions found in \gls*{dmri} are nonlinear, \emph{bbregister} excludes
  from the boundary search those regions typically warped by the artifact.
This tool has become the standard method for its proven robustness.
Nonlinear registration has been successfully performed between \gls*{t2} and \emph{b0}
  images for their similarity, but uniquely as a way to correct for distortions
  \citep{kybic_unwarping_2000,studholme_accurate_2000,wu_comparison_2008,tao_variational_2009}.
Further registration of \gls*{t1} and \gls*{t2} images was still required to map the anatomical
  information (and the \gls*{wm} segmentation) into \gls*{dmri} space.

To jointly solve registration and segmentation problems such as longitudinal object
  tracking \citep{paragios_level_2003} and atlas-based segmentation 
  \citep{gorthi_active_2011}, active contours have been successfully integrated 
  in image registration methods.
\cite{unal_coupled_2005} and later \cite{wang_joint_2006},
  extended an existing method using linear registration \citep{yezzi_variational_2003}
  to the nonlinear case implementing a free deformation field.
\cite{droske_mumfordshah_2009} reviewed the latter set of techniques, and proposed two different
  approaches to apply the Mumford-Shah functional \citep{mumford_optimal_1989} in simultaneous
  registration and segmentation, through the propagation of the deformation field from
  the contours to the whole image definition.
Recently, \cite{guyader_combined_2011} proposed a simultaneous segmentation and
  registration method using level sets and a nonlinear elasticity smoother on the
  displacement vector field, which preserves topology even with very large deformations.
Finally, \cite{gorthi_active_2011} extended the existing methodologies using a multiphase
  level-set function for the registration of several active contours, in the application
  of atlas-based segmentation.

The hypothesis under this research is that the registration and segmentation
  problems in \gls*{dmri} can be solved simultaneously, increasing the geometrical
  accuracy of the process.
We propose a tool called \emph{regseg} to exploit the prior information of shapes
  extracted on \gls*{t1} images to register the anatomical reference
  to \gls*{dmri} space, implicitly segmenting these data.
The approach uses active contours without edges \citep{chan_active_2001} that evolve driving a
  free-deformation field of B-Spline functions.
Optimization is performed using a descent strategy of shape-gradients
  \citep{besson_dream2s_2003,herbulot_segmentation_2006}, therefore \emph{regseg}
  does not implement levelsets as most of the presented methods.
The nonlinear warping caused by distortion is aligned with one of the imaging axis due
  to the theory underpinning \gls*{epi} sequences.
Therefore, \emph{regseg} includes an anisotropic regularizer of the displacement field 
  proposed by \cite{nagel_investigation_1986}.
Finally, we present an instrumentation framework to evaluate correction and
  segmentation pipelines using realistic distortions as ground truth.
With the integration of \emph{regseg} and an in-house implementation of the 
  \gls*{t2b} correction in the framework, we compare the performance
  of both solutions.

>>>>

% -*- root: 00-main.tex -*-
\section{Introduction}\label{sec:introduction}
The accurate delineation of \gls*{wm} in \gls*{dmri} and the fusion of prior
  anatomical information extracted from a \gls*{t1} image of the same subject
  are crucial in a range of applications based on tractography, such as
  the extraction of structural connectivity \citep{craddock_imaging_2013} or
  tract-based spatial statistics \citep{smith_tractbased_2006}.
However, segmenting \gls*{dmri} data precisely and coregistration of anatomical
  images are difficult for several reasons.
First, \gls{dmri} images suffer from partial voluming of several tissues in 
  interfacing voxels due to the low resolution of images (generally around
  \isores[mm]{2.2}).
Second, \gls*{dmri} schemes probe the diffusion process within the brain in 
  many angles called \glspl*{dwi}, completed by one or more baseline (\emph{b0}) 
  volumes without directional gradients.
The extremely low \gls*{snr} and high dimensionality of \glspl*{dwi} disable their
  use for direct segmentation.
The low contrast between \gls*{gm} and \gls*{wm} in the \emph{b0} volumes is not suitable for 
  segmentation either.
Lastly, \gls*{dmri} images are acquired using \gls*{epi} to speed up acquisition
  at the cost of presenting geometrical distortion and 
  signal losses \citep{jezzard_correction_1995} that hinder the segmentation by
  registering an anatomical image as source of same-subject prior information.
The artifact has been proven to cause an important impact on the anatomy extracted
  from \gls*{dmri} \citep{irfanoglu_effects_2012}, particularly in certain fiber bundles
  when used in whole-brain tractography.

@@

To solve the segmentation problem through registration, \cite{saad_new_2009} 
  used Pearson correlation to perform linear alignment of the \gls*{t1} and 
  the \emph{b0}.
Similarly, an also linear registration method is \emph{bbregister} \citep{greve_accurate_2009}.
It uses active contours with edges to look for intensity boundaries in the \emph{b0}
  image.
The active contours are initialized by surfaces extracted from the 
  \gls*{t1} using \emph{FreeSurfer} \citep{fischl_freesurfer_2012}:
  the \emph{pial} surface (exterior of cortical \gls*{gm}) and the \emph{white}
  surface (the \gls*{wm}/\gls*{gm} interface). 
Since the \emph{b0} image only presents a detectable frontier for the pial surface,
  \emph{bbregister} is limited to align the cortical layer in this
  application.
This tool has become the standard method for its proven robustness, despite the 
  distortions found in \gls*{dmri} are nonlinear.
To overcome this issue, \emph{bbregister} excludes from the boundary search those
  regions typically warped by the artifact.
As the distortion is not accounted for, it should be addressed separately.
Nonlinear registration has been successfully performed between \gls*{t2} and \emph{b0}
  images for their similarity, but uniquely as a way to correct for distortions
  \citep{kybic_unwarping_2000,studholme_accurate_2000,wu_comparison_2008,tao_variational_2009}.
Further registration of \gls*{t1} and \gls*{t2} images was still required to map the anatomical
  information (and the \gls*{wm} segmentation) into \gls*{dmri} space.

Therefore, given the described circumstances, a method performing simultaneously
  segmentation in \gls*{dmri} space and registration of the corresponding \gls*{t1} image
  to \gls*{dmri} data could provide the optimal solution.
Previously, joint segmentation and registration has been successfully applied to
  longitudinal object tracking \citep{paragios_level_2003} and atlas-based
  segmentation \citep{gorthi_active_2011}.
The most extended approach is integrating active contours in image registration 
  methods.
\cite{unal_coupled_2005} and later \cite{wang_joint_2006},
  improved an existing method \citep{yezzi_variational_2003} based on linear registration
  to the nonlinear case implementing a free-form deformation field.
\cite{droske_mumfordshah_2009} reviewed the latter set of techniques, and proposed two different
  approaches to apply the Mumford-Shah functional \citep{mumford_optimal_1989} in simultaneous
  registration and segmentation, through the propagation of the deformation field from
  the contours to the whole image definition.
Recently, \cite{guyader_combined_2011} proposed a 2D simultaneous segmentation and
  registration method using level sets and a nonlinear elasticity smoother on the
  displacement vector field, which preserves topology even with very large deformations.
Finally, \cite{gorthi_active_2011} extended the existing methodologies using a multiphase
  level-set function for the registration of several active contours, in the application
  of atlas-based segmentation.

The hypothesis under this research is that the registration and segmentation
  problems in \gls*{dmri} can be solved simultaneously, increasing the geometrical
  accuracy of the process.
We propose a tool called \emph{regseg} to exploit the prior information of shapes
  extracted on \gls*{t1} images to register the anatomical reference
  to \gls*{dmri} space, implicitly segmenting these data.
The approach uses active contours without edges \citep{chan_active_2001} that evolve driving a
  free-deformation field of B-Spline functions.
Optimization is performed using a descent strategy of explicit shape-gradients
  \citep{besson_dream2s_2003,herbulot_segmentation_2006}, therefore \emph{regseg}
  does not implement levelsets as most of the presented methods.
The nonlinear warping caused by distortion is aligned with one of the imaging axis due
  to the theory underpinning \gls*{epi} sequences.
Therefore, \emph{regseg} includes an anisotropic regularizer of the displacement field 
  proposed by \cite{nagel_investigation_1986}.
Finally, we present an instrumentation framework to evaluate correction and
  segmentation pipelines using realistic distortions as ground truth.
With the integration of \emph{regseg} and an in-house implementation of the 
  \gls*{t2b} correction in the framework, we compare the performance
  of both solutions.

### 2015-04-04 Publications/2015-NeuroImage/04-methods.tex
my changes

% -*- root: 00-main.tex -*-
\section{Methods}
\label{sec:methods}
%
Let $\gammaset = \{\Gamma_m: m \in \mathbb{N}, m \leq N_c\}$ be the set of $N_c$ surfaces
  extracted from the undistorted \gls*{t1} image (the reference space $R$).
Distortion can be rendered as a registration problem where we look for an underlying deformation 
  field $U_s$, mapping $R$ (with $\gammaset \subset R$) to the corresponding features in the distorted 
  \gls*{dmri} images (the moving space $M$):

  \begin{align}
  U_s\colon R \subset \mathbb{R}^n &\to M \subset \mathbb{R}^n \notag\\
  \vec{r} &\mapsto \vec{r}' =\vec{r}+\vec{u}(\vec{r}),
  \label{eq:transform}
  \end{align}
%
  where $\vec{r}$ denotes a position in $R$, $\vec{r}'$ is
  its corresponding location in $M$, and $n$ the dimensionality of images.
Finally, $\vec{u} = \vec{u}(\vec{r})$ is the displacement of every point with respect
  to the reference domain.

@@

The best estimate $\hat{U}$ then fulfills the maximum a posteriori criterium
  \citep{bishop_pattern_2006}, and aligns \gammaset into $M$.
First, we assume independence between pixels, and thus break down the
  global data likelihood into a product of pixel-wise conditional probabilities:

@@

\paragraph*{Deformation model}\label{sec:deformation_model}
Since the vertices of the surfaces $\{\vec{v}_i: \vec{v}_i \subset \gammaset \}_{i=1 \ldots V}$
  likely lay off-grid, it is required to derive $u(\vec{v}_i)$ from a discrete set of parameters
  $\{\vec{u}_k\}_{k=1 \ldots K}$.
Densification is achieved through a set of associated basis functions $\psi_k$.
In our implementation, $\psi_k$ is chosen to be a tensor-product B-Spline kernel
  of degree 3: % ($\beta_3$).

@@

  \begin{align}
  \frac{\partial E(\vec{u})}{\partial \vec{u}_k} &=
  \frac{ \partial }{\partial \vec{u}_k} \Big\{
  \underset{l}{\sum} \int_{\Omega_l} \mdist{f'}{l} \,d\vec{r} \, + \notag\\
  &+ \int_{\Omega} \frac12 [ \boldsymbol{\alpha} \cdot \vec{u}^{\circ2}
  + \boldsymbol{\beta} \cdot (\nabla \vec{u})^{\circ2} ] \,d\vec{r}
  \Big\}.
  \label{eq:gradient_descent}
  \end{align}
%
  where $\vec{u}^{\circ2} = \vec{u}^T \cdot \vec{u}$.
Then, the data and regularization terms are split and discretized to compute their
  derivatives.
The intermediate steps to get to \eqref{eq:gradient_descent} from \eqref{eq:final_gradient} are
  detailed in the \suppl{equations SM6-SM12}:

  \begin{align}
  \frac{\partial E(\vec{u})}{\partial \vec{u}_k} &=
  \vec{g}_k  + \boldsymbol{\alpha} \cdot \vec{u}_k + \boldsymbol{\beta} \cdot (\Delta \vec{u}_k).
  \label{eq:final_gradient}
  \end{align}

@@

  \begin{align}
  \vec{u}_k^{t+1} = \mathcal{F}^{-1}\left\{ \frac{\mathcal{F}\{\delta^{-1} \, \vec{u}_k^t + \vec{g}_k\} }%
                  {\mathcal{F}\{(\delta^{-1} - \boldsymbol{\alpha})\, I-\boldsymbol{\beta}\Delta\}} \right\}
  \label{eq:update_equation}
  \end{align}

\paragraph*{Settings, implementation details, and convergence}
\label{sec:conv_report}
The registration parameters (such as $\delta$, $\boldsymbol{\alpha}$, $\boldsymbol{\beta}$,
  the B-Spline grid resolutions, target image smoothing, etc.)
  and other implementation details (for instance the sparse matrix approach
  to fast interpolation) are discussed in the \suppl{section S1}.
The actual choices of parameter settings are publicly distributed with the source code of the experiments.
Additionally, we release our software along with a tool for generating convergence reports to
  demonstrate the behavior of \emph{regseg} and help scientists configure their own experiments.
One sample report is found in the \suppl{section S1.3}.

\subsection{Experiments and evaluation}
\label{sec:experiments_evaluation}
%
In order to demonstrate the performance of \emph{regseg}, we first conducted a battery of
  accuracy tests over synthetic data, and then applied it in the susceptibility distortion
  correction of real data.
\autoref{fig:evworkflows} presents the workflow implementing the evaluation instruments.
Besides a visual assessment of the results, we report quantitative evaluations using
  two metrics.
In the case of the phantoms, since we had produced distortions along the three
  available dimensions, we computed the Haussdorf distance, by reusing the
  ``point-to-cell'' method of \cite{commandeur_vtk_2011}.
Conversely, the susceptibility-derived distortions only happen along the \gls*{pe}
  axis of the image.
Therefore, a \gls*{swindex} can be computed as the one-to-one distance between corresponding
  vertices of surfaces, weighted by their respective Voronoi area $a_i$:

@@

Selecting the appropriate labels in the \emph{aparc} segmentation, we applied
  \texttt{mri\_tessellate} to extract the surface of the following
  six homogeneous regions $\Omega_l$:
  1) the thalamus, $\Gamma_{Tha}$;
  2) \gls*{csf} of the ventricular system and deep \gls*{gm} structures, $\Gamma_{VdGM}$;
  3) cerebral \gls*{wm}, $\Gamma_{WM}$;
  4) brain stem and cerebellar \gls*{wm}, $\Gamma_{bst}$;
	5) cerebellar \gls*{gm}, $\Gamma_{cbGM}$; and
	6) cortical \gls*{gm} surface, $\Gamma_{pial}$.
The choice of this particular model is further addressed in \autoref{sec:res_model_and_metric}.

The displacements along the \gls*{pe} axis are related to the local field
  deviation $\Delta B_0(\vec{r})$ \citep{jezzard_correction_1995}:

  \begin{equation}
  u(\vec{r}) = \frac{\gamma \, T_{acq}\, s_{PE}}{2\pi}\Delta B_0(\vec{r}) \: \hat{\vec{e}}_{PE},
  \label{eq:fieldmap}
  \end{equation}
%
where $\gamma$ is the gyromagnetic ratio, $T_{acq}$ is the readout time,
  $s_{PE}$ is the pixel size along \gls*{pe}, and $\hat{\vec{e}}_{PE}$ the unitary
  vector along \gls*{pe}.

In this case, we derived the deformation $U_{true}$ from the field maps released with
  the corresponding packages of each dataset from the \gls*{hcp} applying \eqref{eq:fieldmap},
  mimicking the real distortions, using a derivation of our previous work
  \citep{esteban_simulationbased_2014}.
After warping the original \gls*{dmri} with $U_{true}^{-1}$, we computed the \gls*{dti} and
  the derived scalars (\gls*{fa} and \gls*{adc}) using \emph{MRtrix} \citep{tournier_mrtrix_2012}.
The stack of \gls*{fa} and \gls*{adc} conforms the multivariate input for \emph{regseg}.

>>>>

% -*- root: 00-main.tex -*-
\section{Methods}
\label{sec:methods}
%
Let $\gammaset = \{\Gamma_m: m \in \mathbb{N}, m \leq N_c\}$ be the set of $N_c$ surfaces
  extracted from the undistorted \gls*{t1} image (the reference space $R$).
We reformulate the segmentation of the distorted \gls*{dmri} images (the moving space $M$)
  as a registration problem where we look for an underlying deformation field $U$, such that 
  the structures in $R$ defined by \gammaset{} optimally align with their corresponding
  structures in $M$:

  \begin{align}
  U\colon R \subset \mathbb{R}^n &\to M \subset \mathbb{R}^n \notag\\
  \vec{r} &\mapsto \vec{r}' =\vec{r}+\vec{u}(\vec{r}),
  \label{eq:transform}
  \end{align}
%
  where $\vec{r}$ denotes a position in $R$, $\vec{r}'$ is
  its corresponding location in $M$, and $n$ the dimensionality of images.
Finally, $\vec{u} = \vec{u}(\vec{r})$ is the displacement of every point with respect
  to the reference domain.

@@

The best estimate $\hat{U}$ then fulfills the maximum a posteriori criterium
  \citep{bishop_pattern_2006}, and aligns \gammaset{} into $M$.
First, we assume independence between pixels, and thus break down the
  global data likelihood into a product of pixel-wise conditional probabilities:

@@

\paragraph*{Deformation model}\label{sec:deformation_model}
Since the vertices of the surfaces $\{\vec{v}_i: \vec{v}_i \subset \gammaset \}_{i=1 \ldots N_v}$
  likely lay off-grid, it is required to derive $u(\vec{v}_i)$ from a discrete set of parameters
  $\{\vec{u}_k\}_{k=1 \ldots K}$.
Densification is achieved through a set of associated basis functions $\psi_k$.
In our implementation, $\psi_k$ is chosen to be a tensor-product B-Spline kernel
  of degree 3: % ($\beta_3$).

@@

  \begin{align}
  \frac{\partial E(\vec{u})}{\partial \vec{u}_k} &=
  \frac{ \partial }{\partial \vec{u}_k} \Big\{
  \underset{l}{\sum} \int_{\Omega_l} \mdist{f'}{l} \,d\vec{r} \, + \notag\\
  &+ \int_{\Omega} \frac12 [ \boldsymbol{\alpha} \cdot \vec{u}^{\circ2}
  + \boldsymbol{\beta} \cdot (\nabla \vec{u})^{\circ2} ] \,d\vec{r}
  \Big\}.
  \label{eq:gradient_descent}
  \end{align}
%
  where $\vec{u}^{\circ2} = \vec{u}^T \cdot \vec{u}$.
Then, the data and regularization terms are split and discretized to compute their
  derivatives.
The computation of the explicit shape gradients at each $\vec{v}_i'$ is described in \autoref{fig:method}.
The intermediate steps to get to \eqref{eq:final_gradient} from \eqref{eq:gradient_descent} are
  detailed in the \suppl{equations SM6-SM12}:

  \begin{align}
  \frac{\partial E(\vec{u})}{\partial \vec{u}_k} &=
  \vec{g}_k  + \boldsymbol{\alpha} \cdot \vec{u}_k - \boldsymbol{\beta} \cdot (\Delta \vec{u}_k).
  \label{eq:final_gradient}
  \end{align}

@@

  \begin{align}
  \vec{u}_k^{t+1} = \mathcal{F}^{-1}\left\{ \frac{\mathcal{F}\{\delta^{-1} \, \vec{u}_k^t + \vec{g}_k\} }%
                  {\mathcal{F}\{(\delta^{-1} + \boldsymbol{\alpha})\, I - \boldsymbol{\beta}\Delta\}} \right\}
  \label{eq:update_equation}
  \end{align}

\paragraph*{Implementation details, settings and convergence}
\label{sec:conv_report}
The \emph{regseg} tool includes a multiresolution strategy on the free-form deformation field.
Registration pyramids are created by setting the spacing between control points of the B-Spline basis
  functions for each level of the multiresolution.
This implementation detail, along with other features (as the sparse matrix approach
  to fast interpolation) and the main parameters 
  (such as $\delta$, $\boldsymbol{\alpha}$, $\boldsymbol{\beta}$, the B-Spline grid resolutions,
  target image smoothing, etc.) are discussed in the \suppl{section S1}.
The actual choices of parameter settings are publicly distributed with the source code of the experiments.
These final settings were manually obtained based on the feedback of post-registration convergence
  reports (as the one found in the \suppl{section S1.3}).
We release \emph{regseg} along with the tool for generating the convergence report.

\subsection{Experiments and evaluation}
\label{sec:experiments_evaluation}
%
In order to demonstrate the performance of \emph{regseg}, we first conducted a battery of
  accuracy tests over synthetic data, and then applied to real \gls*{dmri} data.
\autoref{fig:evworkflows} presents the workflow implementing the evaluation instruments.
Besides a visual assessment of the results, we report quantitative evaluations using
  two metrics.
In the case of the phantoms, since we had produced distortions along the three
  available dimensions, we computed the Haussdorf distance, by reusing the
  ``point-to-cell'' method of \cite{commandeur_vtk_2011}.
Conversely, the susceptibility-derived distortions only happen along the \gls*{pe}
  axis of the image.
Therefore, a \gls*{swindex} can be computed as the one-to-one distance between corresponding
  vertices of surfaces, weighted by their respective Voronoi area $a_i$:

@@

Selecting the appropriate labels in the \emph{aparc} segmentation, we applied
  \texttt{mri\_tessellate} to extract the surface of the following
  six homogeneous regions $\Omega_l$:
  1) the thalamus, $\Gamma_{Tha}$;
  2) \gls*{csf} of the ventricular system and deep \gls*{gm} structures, $\Gamma_{VdGM}$;
  3) cerebral \gls*{wm}, $\Gamma_{WM}$;
  4) brain stem and cerebellar \gls*{wm}, $\Gamma_{bst}$;
	5) cerebellar \gls*{gm}, $\Gamma_{cbGM}$; and
	6) cortical \gls*{gm} surface, $\Gamma_{pial}$.
The segmentation model corresponding to this selection of surfaces is presented in
  \autoref{fig:model}, and further addressed in \autoref{sec:res_model_and_metric}.

The displacements along the \gls*{pe} axis are related to the local deviation of the
  field $\Delta B_0(\vec{r})$ \citep{jezzard_correction_1995}:

  \begin{equation}
  u(\vec{r}) = \frac{\gamma \, T_{acq}\, s_{PE}}{2\pi}\Delta B_0(\vec{r}) \: \hat{\vec{e}}_{PE},
  \label{eq:fieldmap}
  \end{equation}
%
where $\gamma$ is the gyromagnetic ratio, $T_{acq}$ is the readout time,
  $s_{PE}$ is the pixel size along \gls*{pe}, and $\hat{\vec{e}}_{PE}$ the unitary
  vector along \gls*{pe}.
With certain \gls*{mr} sequences it is possible to estimate $\Delta B_0$, obtaining
  the so-called fieldmap.

In this case, we derived the deformation $U_{true}$ from the fieldmaps released with
  the corresponding packages of each dataset from the \gls*{hcp} applying \eqref{eq:fieldmap},
  mimicking the real distortions, using a derivation of our previous work
  \citep{esteban_simulationbased_2014}.
After warping the original \gls*{dmri} with $U_{true}^{-1}$, we computed the \gls*{dti} and
  the derived scalars (\gls*{fa} and \gls*{adc}) using \emph{MRtrix} \citep{tournier_mrtrix_2012}.
The stack of \gls*{fa} and \gls*{adc} conforms the multivariate input for \emph{regseg}.

### 2015-04-04 Publications/2015-NeuroImage/05-results.tex
my changes

\begin{figure*}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tikzpicture}
        \node[inner sep=10pt, draw=black!40](fig03b) at (0,7.9)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure03-b}};
        \node[inner sep=10pt, draw=black!40](fig03c) at (0,0)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure03-c}};
        \node[circle, text=black!75] at (-9.4,10.6) {\Huge \textbf{A}};
        \node[circle, text=black!75] at (-9.4,3.5) {\Huge \textbf{B}};
      \end{tikzpicture}
    }%
  \caption{A. Visual assessment of the results on the low resolution sets:
    ``gyrus'' (top-left), ``L-shape'' (top-right), ``ball'' (bottom-left),
    and ``box'' at (bottom-right).
  In yellow color, the recovered contours after registration are represented.
  Our method showed high accuracy, as demonstrates almost exact location of the registered
    contours with respect to their ground truth position depicted in green.
  Partial volume effect turns segmentation of the sulci a challenging problem with voxel-wise
    clustering methods, but it is successfully segmented with our method.
  B. Quantitative evaluation of registration error in terms of average Hausdorff distance of
    surfaces at high (left) and low (right) resolutions, demonstrating that the error is
    consistently below the voxel size.
    }\label{fig:phantom}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tikzpicture}
        \node[inner sep=10pt, draw=black!40](fig03b) at (0,7.9)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure03-b}};
        \node[inner sep=10pt, draw=black!40](fig03c) at (0,0)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure03-c}};
        \node[circle, text=black!75] at (-9.4,10.6) {\Huge \textbf{A}};
        \node[circle, text=black!75] at (-9.4,3.5) {\Huge \textbf{B}};
      \end{tikzpicture}
    }%
  \caption{A. Visual assessment of the results on the low resolution sets:
    ``gyrus'' (top-left), ``L-shape'' (top-right), ``ball'' (bottom-left),
    and ``box'' at (bottom-right).
  In yellow color, the recovered contours after registration are represented.
  Our method showed high accuracy, as it demonstrates the almost exact location of the registered
    contours with respect to their ground truth position depicted in green.
  Partial volume effect turns segmentation of the sulci a challenging problem with voxel-wise
    clustering methods, but it is successfully segmented with our method.
  B. Quantitative evaluation of registration error in terms of average Hausdorff distance of
    surfaces at low (left) and high (right) resolutions, demonstrating that the error is
    consistently below the voxel size.
    }\label{fig:phantom}
\end{figure*}
